### 2015-07-01 narrative/eviction-metrics.tex
modified:   eviction-metrics.tex

There is a spectrum of approaches on how to leverage a memory and storage hierarchy: On one end of the spectrum is to copy or move data from one tier to another, the closer the tier to the hierarchy's top, the faster the access to the data it contains. On the other end of the spectrum is to use higher tiers exclusively for auxiliary data that to some extent represents the actual data on the lowest tier. Examples of auxiliary data are views, indices, lossy compressions, lower resolution data, and summary data (sometimes also known as metadata). There are a number of drivers that push

>>>>

\paragraph{Background:} There is a spectrum of approaches on how
to leverage a memory and storage hierarchy: On one end of the
spectrum is to copy or move data from one tier to another, the
closer the tier to the hierarchy's top, the faster the access to
the data it contains. On the other end of the spectrum is to use
higher tiers exclusively for auxiliary data that to some extent
represents the actual data on the lowest tier. Examples of auxiliary
data are views, indices, lossy compressions, lower resolution data,
and summary data (sometimes also known as metadata). There are a
number of drivers that push approaches to one or the other extreme:
(1) if a high tier has sufficient room for an application's working
set, approaches that move the working set into that tier will perform
well; Conversely, if a high tier very rarely captures working sets,
it is better to fill it with auxiliary data that speeds up access
to the working set captured by a lower tier; working sets only
reduce capacity misses but the concept can be generalized to the
likelihood of having the right data in place, i.e. proactively
moving data to high tiers accessed in predictable patterns reduces
compulsory misses as well; (2) if the application generates parallel
read/write requests and strong consistency semantics are important,
approaches that use auxiliary data to speed up access to persistent
shared data might yield better performance than approaches that
require coherence overhead to keep all copies on higher tiers
consistent; (3) if the application's access patterns are mismatched
with low tier access characteristics, a combination of approaches
that use auxiliary data and move data between tiers in order to
convert access patterns into a better match will perform well.

% Any other drivers?

\paragraph{Approach:} This spectrum enables interesting strategies
to manage space pressure on high tiers: instead of just evicting
pieces of data (blocks, pages, objects, files), one can free space
by ``thinning'' data so that accesses within more limited views or
lower resolutions can still occur without misses while requests
outside of views or higher resolutions can leverage the information
stored in auxiliary data. Conversely, data on a high tier can be
``enriched'' (e.g. turned into a higher resolution) if there is
value in doing so.

\paragraph{Related Work:} Mention Stanford's Legion system.

\paragraph{Challenge:} The decision on when to thin and when to
enrich data on a particular level depends on \emph{access patterns}.
Approaches that leveragee access patterns in application at national
labs has shown to greatly improve performance and reduce the amount
of overhead required for data management~\cite{he:hpdc13}. The
challenge is for applications to communicate these access patterns
to the I/O stack layers that manages tiers outside of the address
space. In the proposed work we will develop an abstraction for
\emph{locality} that allow applications or runtime profilers to
describe locality properties of access patterns, and implement
services that leverage locality properties to dynamically determine
the value of thinning or enriching data at a particular tier.
Consider the example of a road navigation system: the locality
properties of each navigation client are based on physical constraints
of speed, direction, likely resolution of map, and the fact that
clients almost never go offroad.
